A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2020-03-13 manuscript.Rmd
advisee to archieve docker image closes #11

There are two ways to share a Docker image; either by sharing the Dockerfile that creates the image, or by sharing the image itself, e.g., through a service like [Dockerhub](https://hub.docker.com). While both ways guarantee a replicable computational environment, sharing the Dockerfile is more transparent; in our workflow, we can use Git to track changes in the Dockerfile (such as updates to dependencies).

>>>>

There are two ways to share a Docker image; either by sharing the Dockerfile that creates the image, or by sharing the image itself, e.g., through a service like [Dockerhub](https://hub.docker.com). While both ways guarantee a replicable computational environment, sharing the Dockerfile is more transparent; in our workflow, we can use Git to track changes in the Dockerfile (such as updates to dependencies). A possible downside is that in order to create an image from a Dockerfile, all software repositories need to be still availible. Hence, to garuntee reproducibility for decades to come, it is best to archieve the binary image at major points of the projets progress e.g. publication with a release on GitHub (see [Version Management] for details).
